% !TEX root = /Users/kartikgohil/Documents/Imperial/Year4/Project/Docs/Final_Report/report_tex/main.tex

\begin{thebibliography}{99}

\bibitem{mimu}
    Mi.Mu Gloves. \emph{Mi.Mu: About}. [Online] Available from: http://mimugloves.bigcartel.com/mi-mu-bio [Accessed 24 Jan 2015].
    
\bibitem{mimugloves}
    Mi.Mu Gloves. \emph{Mi.Mu Collaborator Gloves}. [Online] Available from:  http://mimugloves.bigcartel.com/
    product/collaborator-gloves [Accessed 25 Jan 2015].
    
\bibitem{drumpants}
    DrumPants Inc. \emph{DrumPants}. [Online] Available from: http://www.drumpants.com/ [Accessed 24 Jan 2015].

\bibitem{drumpantsprice}
    DrumPants Inc. \emph{DrumPants}. [Online] Available from: https://legacy.trycelery.com/shop/drumpants [Accessed 25 Jan 2015].

\bibitem{gesturering}
    Logbar Inc. \emph{Ring}. [Online] Available from: http://logbar.jp/ring/en [Accessed 25 Jan 2015].
    

\bibitem{arduinopic}
    Arduino. \emph{Arduino Uno}. [Online] Available from: http://arduino.cc/en/main/arduinoBoardUno [Accessed 28 Jan 2015].
    
\bibitem{hc06ebay}
    Ebay. \emph{5V JY-MCU HC-06 V1.04 Bluetooth Transeiver RF Module Serial Port 51 AVR MCU ARM} [Online] http://www.ebay.com/itm/5V-JY-MCU-HC-06-V1-04-Bluetooth-Transeiver-RF-Module-Serial-Port-51-AVR-MCU-ARM-/261121350024 [Accessed 28 Jan 2015].
    
\bibitem{arduinosite}
    Arduino. \emph{Arduino}. [Online] Available from: http://arduino.cc [Accessed 28 Jan 2015].

\bibitem{pyolibrary}
    Olivier B\'{e}langer, Ajax Sound Studio. \emph{PyO 0.7.3 Documentation > API Documentation > Classes By Category}. [Online] Available from: http://ajaxsoundstudio.com/pyodoc/api/classes/index.html [Accessed 28 Jan 2015].


\bibitem{kingstatedatasheet}
    Premier Farnell plc. \emph{Specification for Approval - KINGSTATE, Electret Condenser Microphone, KEEG1542PBL-A}. [Online] Available from: http://www.farnell.com/datasheets/1780663.pdf [Accessed 12 Jan 2015].


\bibitem{queuelist}

    Efstathios Chatzikyriakidis. \emph{QueueList Library for Arduino}. [Online] Available from: http://playground.arduino.cc/Code/QueueList [Accessed 17 Jan 2015].

\bibitem{queuearray}

    Efstathios Chatzikyriakidis. \emph{QueueArray Library for Arduino}. [Online] Available from: http://playground.arduino.cc/Code/QueueArray [Accessed 17 Jan 2015].

\bibitem{pyserial}
    Chris Liechti, SourceForge. \emph{Welcome to pySerial's documentation}. [Online] Available from: http://pyserial.sourceforge.net [Accessed 29 Jan 2015].

\bibitem{pydub}
    Jiaaro. \emph{Pydub by jiaaro}. [Online] Avaliable from: http://pydub.com [Accessed 1 Feb 2015].

\bibitem{pyaudio}
    Hubert Pham. \emph{PyAudio 0.2.8 documentation > PyAudio Documentation}. [Online] Available from: http://people.csail.mit.edu/hubert/pyaudio/docs/ [Accessed 1 Feb 2015].
    
    
\bibitem{pyasparticle}
    John Glover, Victor Lazzarini, Joseph Timoney. Python For Audio Signal Processing. The Sound and Digital Music Research Group. [Online] 2011. Available from: http://lac.linuxaudio.org/2011/papers/40.pdf [Accessed 1 Feb 2015].

\bibitem{arduinobluetooth}
    techbitar, Instructables. \emph{Cheap 2-Way Bluetooth Connection Between Arduino and PC}. [Online] Available from: http://www.instructables.com/id/Cheap-2-Way-Bluetooth-Connection-Between-Arduino-a/ [Accessed 1 Feb 2015].

\bibitem{rtdsppaper}
    Ferruccio Bettarelli, Emanuele Ciavattini, Ariano Lattanzi, Francesco Piazza, Stefano Squartini, Diego Zallocco. NU-Tech: Implementing DSP Algorithms in a Plug-in Based Software Platform for Real time Audio Applications. [Online] 2005. Available from: http://www.aes.org/e-lib/browse.cfm?elib=13105\&rndx=768511 [Accessed 2 Feb 2015].

\bibitem{spikedetection}
    Scott B. Wilson, Ronald Emerson. Spike detection: a review and comparison of algorithms. \emph{Clinical Neurophysiology}. Volume 113, Issue 12, Pages 1873-1881. [Online] 2002. Available from: http://dx.doi.org/10.1016/S1388-2457(02)00297-3 [Accessed 2 Feb 2015].
    
\bibitem{transientdetectionpaper}
    V. Datta, G.V. Anand. Transient detection in non-Gaussian noise by wavelet packet transform. [Online] 2010. Available from: doi:10.1109/SPCOM.2010.5560494 [Accessed 2 Feb 2015].

\bibitem{wxpython}
Julian Smart, Vadim Zeitlin, Robin Dunn, Stefan Csomor, Bryan Petty, Francesco Montorsi, Robert Roebling et al. \textit{wxWidgets: Documentation}. [Online] 6 Oct 2014. Available from: http://www.wxpython.org/onlinedocs.php [Accessed 10 Jun 2015].

\bibitem{interpolation}
Ryan Metivier. Allegro MicroSystems, LLC. \textit{Method for Converting a PWM Output to an Analog Output When Using Hall Effect Sensor ICs}. [Online] Available from: http://www.allegromicro.com/en/Design-Center/Technical-Documents/Hall-Effect-Sensor-IC-Publications/Method-for-Converting-a-PWM-Output-to-an-Analog-Output-When-Using-Hall-Effect-Sensor-ICs.aspx [Accessed 10 Jun 2015].

\bibitem{analogread}
Arduino. \textit{analogRead()}. [Online] 2015. Available from: http://www.arduino.cc/en/Reference/AnalogRead [Accessed 10 Jun 2015].

\bibitem{juce}
Roli Ltd. \textit{JUCE}. [Online] Available from: https://www.juce.com [Accessed 10 Jun 2015].

\bibitem{introjucer}
Roli Ltd. \textit{The Introjucer}. [Online] Available from: http://www.juce.com/learn/introjucer  [Accessed 10 Jun 2015].

\bibitem{pthread}
Blaise Barney, Lawrence Livermore National Laboratory. \textit{POSIX Threads Programming}. [Online] 6 Apr 2015. Available from: https://computing.llnl.gov/tutorials/pthreads/ [Accessed 10 Jun 2015].

\bibitem{termios}
Wikibooks. \textit{Serial Programming/termios}. [Online] 25 Apr 2015. Available from: http://en.wikibooks.org/wiki/Serial\_Programming/termios [Accessed 10 Jun 2015].

\bibitem{eagle}
Cadsoft \textit{About EAGLE PCB Design Software}. [Online] 2011. Available from: http://www.cadsoftusa.com/eagle-pcb-design-software/about-eagle/ [Accessed 10 Jun 2015].

\bibitem{sketchup}
Trimble Navigation Limited. \textit{SketchUp: The easiest way to draw in 3D}. [Online] 2013. Available from: http://www.sketchup.com [Accessed 10 Jun 2015].

\bibitem{cura}
Ultimaker. \textit{Cura: You And Cura Made For Each Other}. [Online] 2015. Available from: https://ultimaker.com/en/products/software [Accessed 10 Jun 2015].

\bibitem{ultimaker}
Ultimaker. \textit{Ultimaker 2 Family: Our family made to make you smile}. [Online] 2015. Available from: https://ultimaker.com/en/products/ultimaker-2-family [Accessed 10 Jun 2015].

\bibitem{thermalnoise}


\bibitem{groundplane}


\bibitem{oversampling}


\bibitem{codewords}



\bibitem{ts7001}
Touchstone Semiconductor Inc. \textit{TS7001: A Micropower, 2-channel, 187.5-ksps, Serial-Output 12-bit SAR ADC}. [Online] Available from: http://www.farnell.com/datasheets/1774447.pdf [Accessed 9 Jun 2015]

\bibitem{microusbconnector}
Hirose Electric Co., Ltd. \textit{?Micro-USB connectors meeting USB 2.0 Standard: ZX Series}. [Online] Available from: http://docs-europe.electrocomponents.com/webdocs/1363/0900766b81363588.pdf [Accessed 9 Jun 2015]

\bibitem{microusbcable}
Roline. \textit{ROLINE USB 2.0 Cable, USB Type A M - Micro USB B M 1.8 m}. [Online] Available from: http://docs-europe.electrocomponents.com/webdocs/125b/0900766b8125b918.pdf [Accessed 9 Jun 2015]

\end{thebibliography}